Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure

### 2012-04-18 paper.tex
Added Ibs reactor figure. Increased size of some figures.
Larger figures fits better in the layout used for manuscripts
used for submission to ACS-Nano.

The experiments were performed in Si-based 20x16\,mm $\mu$-reactors\cite{Henriksen2009}. The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide, 3\,$\mu$m high and 1500\,$\mu$m long capillary used for sniffing gases from the reactor volume. The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate in a pressure range of 0--2.5\,bar. The reaction gases are supplied to the two inlets by flow controllers capable of controlling the gas flow from 0--10 mL/min. The capillary flow is fed into a quadropole mass-spectrometer (QMS) for analysis while any surplus of gas from the inlets is passed directly through to the outlet via a pressure controller allowing control of reactor pressure. The design makes sure that all gases exposed to the catalyst under investigation are measured by the QMS ensuring an extremely high sensitivity of the system. 
\begin{scheme}
  \includegraphics[width=8cm]{reactor.jpg}
  \caption{Image of the 20x16\,mm microreactor showing the circular reactor area and gas channel system}
  \label{fgr:reactor}
\end{scheme}
Before any measurements are performed the reactor is pumped by a turbopump to minimize contaminants in the system. When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operation at $1\,$bar in the reactor volume the pressure is $\sim5\times10^{-7}\,$mbar in the QMS chamber.

@@

\begin{scheme}
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample. After performing a light-off ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place. The non-zero value of CO during high conversion periods is consistent with the expected QMS background signals from CO$_2$ and O$_2$.}
  \label{fgr:initial_treatment}
\end{scheme}

@@

\begin{scheme}
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate deactivation. For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself. This extremely long oscillation period is not commonly seen and was a result of careful parameter tuning. Typical oscillation periods are normally between $\sim$30\,s and $\sim$30\,min. Inserted circles illustrates the proposed model. At high conversion the platinum is oxidized (red) while in low conversion the sample is reduced (blue).}
  \label{fgr:full_oscillation}
\end{scheme}

@@

\begin{scheme}
  \includegraphics[width=9cm]{summary_of_long_measurement.png}
  \caption{Summary of the oscillation period as a function of time for a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days. Time is defined from experiment start and hence includes initial treatment. The inset shows the initial steady increase in oscillation period.}
  \label{fgr:long_measurement}
\end{scheme}

Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations extracted from the same four days measurement. Data from shortly after the initial treatment, after 2800\,min of oscillation time and after 5900\,min are shown. After 5900\,min the oscillations are more irregular which is consistent with the data shown in Figure \ref{fgr:long_measurement}. Also, oscillations in between full conversion oscillations with smaller amplitude and much higher frequency than the full on-off cycles become more visible as time progresses.
\begin{scheme}
  \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
  \caption{Extracts from the 4 days long experiment. The oscillation period becomes more irregular with time while the total integrated conversion remains constant. Furthermore, small oscillations in between full conversion cycles become more prominent as time progresses.}
  \label{fgr:extracts}
\end{scheme}

@@

\begin{scheme}
  \includegraphics[width=9cm]{temperature_dependence.png}
  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C. Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s.}
  \label{fgr:temperature_dependence}
\end{scheme}

@@

\begin{scheme}
  \includegraphics[width=9cm]{oscillations_gas_dependence_summary_supplemental.png}
  \caption{Summary of the gas-dependence. The overall trend of increasing oscillation period is now supporimposed by small discontinous stpes when the CO concentration is increased.}
  \label{fgr:gas_dependence_summary}
\end{scheme}

@@

\begin{scheme}
\centering
  \includegraphics[width=9cm]{temperature_dependence_supplemental.png}
  \caption{Another example of the very pronounced temperature dependence.}
  \label{fgr:temperature_dependence_supplemental}
\end{scheme}

@@

\begin{scheme}
  \includegraphics[width=9cm]{duty_cycles_long_measurement_supplemental.png}
  \caption{A plot of the duty-cycle of the sample duing the 4-day long experiment. The individual data-points is calculted as the integral of CO (red) or CO$_2$ (blue) doing the individual oscillations. The ratio between CO and CO$_2$ is drawn in black.}
  \label{fgr:duty_cycles_supplemental}
\end{scheme}

>>>>

The experiments were performed in Si-based 20x16\,mm $\mu$-reactors\cite{Henriksen2009}. The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide, 3\,$\mu$m high and 1500\,$\mu$m long capillary used for sniffing gases from the reactor volume. The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate in a pressure range of 0--2.5\,bar. The reaction gases are supplied to the two inlets by flow controllers capable of controlling the gas flow from 0--10 mL/min. The capillary flow is fed into a quadropole mass-spectrometer (QMS) for analysis while any surplus of gas from the inlets is passed directly through to the outlet via a pressure controller allowing control of reactor pressure. The design makes sure that all gases exposed to the catalyst under investigation are measured by the QMS ensuring an extremely high sensitivity of the system. 
\begin{scheme}
  \includegraphics[width=8cm]{Ib-reactor.png}
  \caption{Image of the 20x16\,mm microreactor showing the circular reactor area and gas channel system}
  \label{fgr:reactor}
\end{scheme}
Before any measurements are performed the reactor is pumped by a turbopump to minimize contaminants in the system. When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operation at $1\,$bar in the reactor volume the pressure is $\sim5\times10^{-7}\,$mbar in the QMS chamber.

@@

\begin{scheme}
  \includegraphics[width=12cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample. After performing a light-off ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place. The non-zero value of CO during high conversion periods is consistent with the expected QMS background signals from CO$_2$ and O$_2$.}
  \label{fgr:initial_treatment}
\end{scheme}

@@

\begin{scheme}
  \includegraphics[width=16cm]{single_full_oscillation.png}
  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate deactivation. For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself. This extremely long oscillation period is not commonly seen and was a result of careful parameter tuning. Typical oscillation periods are normally between $\sim$30\,s and $\sim$30\,min. Inserted circles illustrates the proposed model. At high conversion the platinum is oxidized (red) while in low conversion the sample is reduced (blue).}
  \label{fgr:full_oscillation}
\end{scheme}

@@

\begin{scheme}
  \includegraphics[width=12cm]{summary_of_long_measurement.png}
  \caption{Summary of the oscillation period as a function of time for a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days. Time is defined from experiment start and hence includes initial treatment. The inset shows the initial steady increase in oscillation period.}
  \label{fgr:long_measurement}
\end{scheme}

Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations extracted from the same four days measurement. Data from shortly after the initial treatment, after 2800\,min of oscillation time and after 5900\,min are shown. After 5900\,min the oscillations are more irregular which is consistent with the data shown in Figure \ref{fgr:long_measurement}. Also, oscillations in between full conversion oscillations with smaller amplitude and much higher frequency than the full on-off cycles become more visible as time progresses.
\begin{scheme}
  \includegraphics[width=12cm]{extracts_from_very_long_oscillation.png}
  \caption{Extracts from the 4 days long experiment. The oscillation period becomes more irregular with time while the total integrated conversion remains constant. Furthermore, small oscillations in between full conversion cycles become more prominent as time progresses.}
  \label{fgr:extracts}
\end{scheme}

@@

\begin{scheme}
  \includegraphics[width=12cm]{temperature_dependence.png}
  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C. Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s.}
  \label{fgr:temperature_dependence}
\end{scheme}

@@

\begin{scheme}
  \includegraphics[width=12cm]{oscillations_gas_dependence_summary_supplemental.png}
  \caption{Summary of the gas-dependence. The overall trend of increasing oscillation period is now supporimposed by small discontinous stpes when the CO concentration is increased.}
  \label{fgr:gas_dependence_summary}
\end{scheme}

@@

\begin{scheme}
\centering
  \includegraphics[width=12cm]{temperature_dependence_supplemental.png}
  \caption{Another example of the very pronounced temperature dependence.}
  \label{fgr:temperature_dependence_supplemental}
\end{scheme}

@@

\begin{scheme}
  \includegraphics[width=12cm]{duty_cycles_long_measurement_supplemental.png}
  \caption{A plot of the duty-cycle of the sample duing the 4-day long experiment. The individual data-points is calculted as the integral of CO (red) or CO$_2$ (blue) doing the individual oscillations. The ratio between CO and CO$_2$ is drawn in black.}
  \label{fgr:duty_cycles_supplemental}
\end{scheme}
